\EVOSUITE at the SBST 2017 Tool Competition

### 2018-01-30 papers/sbst18/paper_sbst18.tex
2018

\begin{abstract}
  \EVOSUITE is a search-based tool that automatically generates unit
  tests for Java code.  This paper summarises the results and
  experiences of \EVOSUITE's participation at the fifth unit testing
  competition at SBST 2017, where \EVOSUITE achieved the highest
  overall score.
\end{abstract}

@@

\begin{table*}[t]
  \centering
  \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes.}
\resizebox{\textwidth}{!}{  
\input{mainTable.tex}
}	
\end{table*}

>>>>

\begin{abstract}
  \EVOSUITE is a search-based tool that automatically generates unit
  tests for Java code.  This paper summarises the results and
  experiences of \EVOSUITE's participation at the fifth unit testing
  competition at SBST 2018, where \EVOSUITE achieved the highest
  overall score.
\end{abstract}

@@

\begin{table*}[t]
  \centering
  \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes.}
\resizebox{0.7\textwidth}{!}{  
\input{mainTable.tex}
}	
\end{table*}
